Estimation of Stochastic Wilson and Cowan Neural Field Model using Expectation Maximisation Algorithm

### 2011-07-12 ltx/data_paper/DataPaper.tex
edits to result section
edit to correlation analysis

From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required. Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small. Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively. If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} might generate numerical error.  However, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving 

@@

\caption{{\bf Cross-section of disturbance covariance support estimation}. The true and the estimated width are shown by solid and dashed lines respectively.}

>>>>

From \eqref{eq:EM-MMGFourier2}, to calculate the exact shape of the disturbance covariance function, observation noise variance and the sensor kernel support are required. Again if the signal to noise ratio is high the effect of $\sigma_{\varepsilon}$ would be small. Note the first bracket and the denominator in \eqref{eq:EM-MMGFourier2} are non-negative power spectral denisties of the noise free observations at time $t+1$ and $t$ respectively. If $m$ is a point sensor then the spatial support of $\gamma$ can be calculated directly, when considering a sensor with a spatial extent, dividing by $\tilde{m}(\boldsymbol\iota)$ in \eqref{eq:EM-MMGFourier2} is then required. Alternatively, assuming a Gaussian shape for disturbance function and sensor kernel (with known support), the support of the disturbance covariance function, $\sigma^2_d$ can be determined analytically using the expression for Gaussian basis functions' convolution, giving 

@@

\caption{{\bf Cross-section of disturbance covariance support estimation}. The normalized true and the estimated width are shown by solid and dashed lines respectively.}
